Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-27 outputs/paper/paper.Rmd
citation updated

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

>>>>

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr], `scales` [@scales] was used to format this report.
